---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggcommonality

<!-- badges: start -->
<!-- badges: end -->

The goal of ggcommonality is to produce bar plots of unique and joint effects 
from commonality analyses. The function outputs a bar plots with unique and 
common effects for each commonality partition. The function is scalable and takes
formula notation for input. This package is very fresh, so its functionality is quite limited.

## Installation

You can install the development version of ggcommonality from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("cmndrsn/ggcommonality")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE}
library(ggcommonality)
# import data
data(mtcars)
# fit model with yhat
yhat_model <- yhat::regr(
  lm(
    formula = mpg ~ cyl + disp + vs + drat,
    data = mtcars
    )
  )
ggcommonality(yhat_model) +
  ggplot2::theme_bw()
```
We can compare the bar plot output to the unique and common effects from the model:

```{r commonality, warning=FALSE}
knitr::kable(yhat_model$Commonality_Data$CC)
```
