---
title: "Advanced ggcommonality"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{advanced-ggcommonality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
```

```{r setup}
library(ggcommonality)
```

# Advanced plotting

ggcommonality provides a flexible interface for stacking unique and common effects, and defining confidence intervals.

When we have both positive and negative effects, defining a confidence interval for our barplot can be somewhat confusing. Let's see how we can work around this.

First, we'll define our GGCommonality object, and plot the output

```{r}
my_formula <- mpg ~ wt + hp + cyl + gear

p <- ggcom(
  my_formula, 
  data = mtcars, 
  stack = 'common'
)

plot(p)
```

## Confidence intervals with positive and negative effects

When defining confidence intervals, ggcommonality by default ignores negative commonalities:

```{r}
plot(p) + ggcom_ci(p)
```

However, we can override this behaviour by specifying the sign argument. Leaving this empty will plot confidence intervals based on both positive and negative effects from our bootstrap simulation:

```{r}
plot(p) + ggcom_ci(p, sign = "")
```

As you can see, this pulls the confidence interval for common effects down in the visualization above. We can also add separate confidence intervals for both positive and negative effects:

```{r}
plot(p) + ggcom_ci(p, sign = "+") + ggcom_ci(p, sign = "-")
```

## Defining confidence intervals

### CI types

ggcommonality uses percentile-based 95% confidence intervals. However, we can specify these in several ways. First, we can choose to use fixed, random, or wild-type confidence intervals. For this, we'll have to redefine our ggcommonality object

```{r}

p1 <- ggcom(
  my_formula, 
  data = mtcars, 
  stack = 'common', 
  resample_type = "fixed"
)
p2 <- ggcom(
  my_formula, 
  data = mtcars, 
  stack = 'common', 
  resample_type = "random"
)
p3 <- ggcom(
  my_formula,
  data = mtcars, 
  stack = 'common', 
  resample_type = "wild"
)
```

We can see how this affects the width of confidence intervals:

```{r}
library(patchwork)
plot(p1) + ggcom_ci(p1) + ggtitle("Fixed") + theme(legend.position = "none") |
  plot(p2) + ggcom_ci(p2) + ggtitle("Random") + theme(legend.position = "none")  |
  plot(p3) + ggcom_ci(p3) + ggtitle("Wild") + theme(legend.position = "none") 
```

### CI width

We may not always want to use 95% confidence intervals. What if we instead want to use a 99% interval? We can specify this behaviour using the ci_bounds argument when defining the ggcommonality object:

```{r}
# define a 99% confidence interval
q <- p

slot(q, "ci_bounds") <- c(0.01, 0.99)

```

Now let's compare:

```{r}
plot(p) + ggcom_ci(p) + ggtitle("95%") + theme(legend.position = "none") |
plot(q) + ggcom_ci(q) + ggtitle("99%") + theme(legend.position = "none") 
```

As expected, our 99% confidence interval is wider.

### Customizing error bars

ggcommonality uses the ggplot2. As such, you can customize your error bars to your heart's content:

```{r}
plot(p) + ggcom_ci(p, width = 0.5, colour = 'grey45')
```

### Customizing barplots

Similarly, we can customize the barplot using ggplot:

```{r}
plot(p) +
  theme_classic()+
  scale_fill_brewer(type = "div", palette = 3)

```
